How reliable are inferences from state-space age-structured assessment models?

### 2023-02-03 Project_0/paper/paper.Rmd
working on Ecov-M simulation code

@@

@@

@@

>>>>

Currenlty, initial population is configured at the equilibrium distribution fishing at $F = 2.5\times F_{\text{MSY}}$.

@@

Steepness and BRPs are not constant when M is time-varying (Miller and Brooks 2021). We uses the a/b parameters for the B-H defined for Fmsy = F40 at the mean M = 0.2 as defined above.

@@

BRPs are not constant when fleet selectivity is time-varying. We uses the a/b parameters for the B-H defined for Fmsy = F40 at the mean of the time series model for selectivity which is the same as the constant selectivity defined above.

@@

\begin{figure}
\caption{Predicted probability of AIC being better for BH model.}\label{glm_res_NAA_re}
\begin{center}
\includegraphics[width = \textwidth]{pred_SR_best_NAA_oms.png}
\end{center}
\end{figure}

## M operating models

### Estimating models include NAA random effects and estimation assumes mean R or BH SR

\begin{table}
\caption{M random effects operating models.}
{\input{M_om_em_R_BH_aic_table}}
\end{table}
\clearpage
